Computing astrophysical inferences with diffusive nested sampling

### 2014-01-05 ms.tex
Random words
Intro sentence

\section{Introduction}

@@

@@

We have been using the following subjective procedure. Later we give two
interpretations of this procedure which may lead the way to less subjective
approaches.
Using DNS we explore the mixture of constrained priors.
\begin{eqnarray}
p_{\rm DNS}(\theta) &=& \sum_{i=1}^n p(\theta)\mathds{1}\left[\mathcal{L} > L^*_i\right]
\end{eqnarray}

>>>>

\section{Introduction}
The major goal of astronomy, as with most sciences, is to understand the
universe as well as we can while recognising that we will never have all of
the relevant information that we might want.

@@

\section{Diffusive Nested Sampling}
DNS is essentially just the Metropolis algorithm. However, instead of the
target distribution being the posterior $p(\pars|\data)$, it is the mixture
of constrained priors.

@@

We have been using the following subjective procedure. Later we give two
interpretations of this procedure which may lead the way to less subjective
approaches.
Using DNS we explore the mixture of constrained priors.
\begin{eqnarray}
p_{\rm DNS}(\theta) &=& \frac{1}{n}\sum_{i=1}^n
\frac{p(\theta)\mathds{1}\left[L(\theta) > L^*_i\right]}{X_i}
\end{eqnarray}
where $X_i \approx e^{-i}$ by construction.
